\begin{ujnabstract*}
\section{ABSTRACT}
\begin{spacing}{1.4}\normalsize{
% 以下为英文摘要，把点引线以下的文字替换成你的就好
% ·································································································
The University has established 4 national-level distinctive specialties,
5 national-level quality courses, 2 national-level exemplary bilingual courses,
2 national-level quality public audio and video courses,
6 specialties training for Outstanding Engineers, 16 provincial-level distinct specialties,
9 specialties jointly supported by the school and enterprise,
53 provincial-level top-grade courses and 5 provincial-level experimental teaching centers.
In recent years, the faculties have undertaken 6 national teaching and research projects and 55 provincial projects,
published 8 textbooks guided by China, and won 3 national "Teaching Achievements" awards and 75 provincial "Teaching and Research Achievements" awards.
In addition, the University has successively won a wide variety of honors for innovation and creativity,
such as the "Challenge Cup" Extracurricular and Academic Contest,
and China Undergraduate Mathematical Contest in Modeling.
The students have won 3133 provincial or national awards,
of which 48 are first prizes and 125 are second prizes at the national level.

In recent years, the university has undertaken 347 national research projects including funds from the National Science and Technology Support Program,
973 project program, 863 project program, and support from the Natural Science Foundation of China,
and Social Science Foundation of China, and 814 provincial projects.
The University has won 238 national and provincial prizes for research achievements,
one second prize of National Award for Technological Invention and 3 second prizes of National Award for Science and Technology Progress,
and obtained 666 national patents. 4799 papers were indexed by SCI, EI or ISTP. 214 academic works,
translations or textbooks were published. Eight journals are currently sponsored by the University of Jinan,
including "China Powder Science and Technology", "Chinese Journal of Cancer Prevention and Treatment",
and "Journal of University of Jinan".
% ·································································································
}\end{spacing}
\begin{spacing}{0.9}
% 以下为关键词的设置，把「keywordn」(n=1,2,3,...)替换成你的关键词就好
\small\enkeywords{congratulations；this is；jida}
\end{spacing}
\end{ujnabstract*}
